\section{Introduction}
\label{sec:intro}

\IEEEPARstart{D}{ecentralized} finance protocols rely on price oracles
to value collateral, settle perpetuals, and trigger liquidations.
Yet the past four years have seen repeated nine-figure exploits in
which attackers manipulated thinly-defended oracle pipelines\,---\,Mango
Markets, bZx, and Cream Finance among them.  Even systems marketed as
``decentralized,'' such as Chainlink Price
Feeds~\cite{breidenbach2021chainlink}, are operated by a small,
permissioned set of reporters whose economic exposure is decoupled
from Ethereum's broader security budget.  If the reporters collude
or are subverted, no on-chain mechanism punishes them at scale.

A natural question is whether the same restaked Ether that already
secures Ethereum consensus could simultaneously back an oracle
service.  EigenLayer answers this affirmatively~\cite{eigenlayer2023}.
In its model, an Actively Validated Service (AVS) is any off-chain
protocol whose participants opt in to slashing of their staked ETH
should they violate the protocol's rules.  EigenLabs ships an
open-source ``Incredible Squaring'' template~\cite{layrlabs_isavs}
that demonstrates the plumbing in miniature: operators receive a
number, return its square, sign the response under BLS12-381, and an
aggregator publishes the quorum-signed answer on chain.  The template
is deliberately a toy.  It is unclear from the template alone how
much engineering effort is required to turn this scaffold into an
economically meaningful service, and what design decisions arise
along the way.

In this work we close that gap by transforming the Incredible
Squaring template into \emph{PriceOracle-AVS}, a working ETH/USD
price oracle whose security derives from EigenLayer restaking.
Operators independently query four major centralized exchanges
(Binance, Coinbase, Kraken, OKX), sign their reports under BLS12-381,
and submit them to an aggregator that computes the statistical
median rather than the mean\,---\,a choice we empirically justify in
Section~\ref{sec:aggregator}.  We propose a deviation slashing rule
that punishes any operator whose individual report deviates from
the median by more than a configurable threshold $\tau$.  We deploy
the full pipeline against a local Anvil testnet and measure its
end-to-end latency, gas cost, and adversarial robustness.

\textbf{Contributions.}  This paper makes three contributions.
\begin{itemize}
  \item We design and implement \emph{PriceOracle-AVS}, a working
        modification of the EigenLabs Incredible Squaring template
        that turns it into a decentralized ETH/USD price oracle.
  \item We propose a \emph{deviation slashing rule} ($\tau{=}5\%$
        in our deployment) and characterize its true-positive vs.\
        false-positive trade-off empirically.
  \item We present an end-to-end evaluation on a local Anvil
        testnet, including BLS gas cost, latency, and a comparison
        against Chainlink Price Feeds.
\end{itemize}

The remainder of the paper is organized as follows.
Section~\ref{sec:background} reviews EigenLayer restaking.
Section~\ref{sec:contracts} presents our smart-contract modifications.
Section~\ref{sec:operator} details the operator implementation.
Section~\ref{sec:aggregator} analyses the BLS aggregation and median
consensus.  Section~\ref{sec:eval} reports end-to-end results,
Section~\ref{sec:discussion} discusses limitations, and
Section~\ref{sec:conclusion} concludes.
