\section{Discussion and Limitations}
\label{sec:discussion}

\subsection{Liveness vs.\ Safety}

Our 67\% quorum threshold (inherited from the Incredible Squaring
template) tolerates up to 33\% of operators going offline without
halting the oracle.  Beyond that point the aggregator simply cannot
publish a response and downstream consumers must fall back to a stale
price\,---\,a clear safety/liveness trade-off.  Lowering the quorum
threshold improves liveness but reduces the cost of a 51\%-style
adversary.  We retain 67\% as a defensible default and leave dynamic
quorum tuning to future work.

\subsection{Per-Task Economic Analysis}

A profitable single-shot price-manipulation attack requires the
adversary to push the on-chain consensus by more than $\tau{=}5\%$,
which by construction triggers slashing on every malicious
operator.  An adversary who under-biases (\textless 5\%) avoids
slashing but obtains only a small expected profit per task; over the
millions of tasks an oracle handles in its lifetime, this is
strictly dominated by simply running an honest operator and
collecting fee revenue.  The remaining attack surface is
\emph{collusion in the majority}, which by EigenLayer's design
requires controlling more than half of the restaked
ETH\,---\,precisely the security assumption Ethereum already
makes for consensus.

\subsection{Comparison with Optimistic Oracles}

UMA's optimistic oracle~\cite{uma2020} takes a different stance: it
assumes a posted price is correct unless explicitly disputed within
a challenge window.  The two models complement each other.
PriceOracle-AVS provides low-latency real-time feeds at modest
on-chain cost; UMA provides high-assurance dispute-driven prices for
infrequent, high-stakes settlements.  A practical DeFi protocol may
well consume both.

\subsection{Future Work}

Three directions stand out.  First, deployment to Ethereum's Holesky
testnet would expose the system to realistic gas markets and operator
diversity.  Second, formal analysis of cascading slashing risk under
the framework of Durvasula and Roughgarden~\cite{durvasula2024robust}
would let us set per-AVS slashing magnitudes that respect a global
solvency budget.  Third, the median rule could be replaced by a
trimmed mean or Theil--Sen estimator, both of which retain the
robustness guarantee of the median while reducing
estimator variance under low-noise conditions.
